---
title: "query 3.1 - Does Popularity Follow Zipf's Distribution"
author: "Mark Berman"
date: "2/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(gamlss.dist)
data <- read.csv("~/cs598_ccc/cassandra_files/queryResults/group3dot1/part-00000-bd06de5d-24f3-4203-857b-d0adfe9e11b7-c000.csv")
str(data)
totalArrivalsAndDepartures <- data$totalArrivalsAndDepartures
rank <- data$rank
probability <- totalArrivalsAndDepartures/sum(totalArrivalsAndDepartures)
airportPopularityRank <- seq(1,length(totalArrivalsAndDepartures))
zipfProbDensity <- dZIPF(airportPopularityRank, mu=1,log=T)
plot(log(airportPopularityRank), zipfProbDensity,type="l",xlab = "log (Airport Popularity rank)", ylab = "log (Probability Density)", col="dodgerblue")
lines(log(rank), log(probability), col="red")
legend(0, -10, legend=c("Fitted Zipf Distribution", "Log-Log (Airport Popularity Rank Probability Distribution"),
       col=c("dodgerblue", "red"), lty=1:2, cex=0.8)
```
The above plot strongly suggests that airport populatiry ran does not follow Zipf's law or a Zipf distribution.   The question is "what disribution does airport popularity come from?"

```{r}
plot(density(totalArrivalsAndDepartures),main="Density estimate of data")
```
```{r}
hist(totalArrivalsAndDepartures,main="Histogram of observed data", ylim=c(0,339), xlim=c(0,13500000),breaks=25, labels=T)
```

```{r}
library(MASS)
data <- read.csv("~/cs598_ccc/cassandra_files/queryResults/group3dot1/part-00000-bd06de5d-24f3-4203-857b-d0adfe9e11b7-c000.csv")
str(data)
totalArrivalsAndDepartures <- data$totalArrivalsAndDepartures
exp_fit <- fitdistr(totalArrivalsAndDepartures, "exponential")
## estimate p value
est_p_value <-  exp_fit$estimate
## estimate goodness of fit
ks.test(totalArrivalsAndDepartures, "pexp", est_p_value)

```

```{r}
plot(density(totalArrivalsAndDepartures),xlim = c(0, quantile(totalArrivalsAndDepartures, 0.99)), main = "Empirical Density vs Fitted Exponential PDF", xlab="airport populatiry rank", sub="N = 339 Bandwidth = 7.62e+04")
lines(totalArrivalsAndDepartures, dexp(totalArrivalsAndDepartures, rate = est_p_value), col = "red")
```

The estimated p_value, the K-S goodness of fit test and the above plot serve to reject the hypothesis that airport popularity rank (measured by total departures and arrivals) follows an
exponential distribution.

```{r}
library(poweRlaw)
data <- read.csv("~/cs598_ccc/cassandra_files/queryResults/group3dot1/part-00000-bd06de5d-24f3-4203-857b-d0adfe9e11b7-c000.csv")
str(data)
totalArrivalsAndDepartures <- data$totalArrivalsAndDepartures
totArrDep_pl = displ$new(totalArrivalsAndDepartures)
est_pl_xmin = estimate_xmin(totArrDep_pl)
totArrDep_pl$setXmin(est_pl_xmin)
totArrDep_ln = dislnorm$new(totalArrivalsAndDepartures)
est_ln_xmin = estimate_xmin(totArrDep_ln)
totArrDep_ln$setXmin(est_ln_xmin)
totArrDep_pois <- dispois$new(totalArrivalsAndDepartures)
est_pois_xmin <- estimate_xmin(totArrDep_pois)
totArrDep_pois$setXmin(est_pois_xmin)
 plot(totArrDep_pl, xlab = "total arrivals and departures", ylab = "ccdf", ylim=c(0.01,1),xlim=c(1,1.3e+07))
 lines(totArrDep_pl, col="red")
 lines(totArrDep_ln, col="green")
 lines(totArrDep_pois, col="dodgerblue", length.out=339)
 legend(1, 0.05, legend=c("powerlaw", "log-normal", "poison"),
       col=c("red", "green", "dodgerblue"), lty=1:2, cex=0.8)


```

```{r}
bs_ln_p = bootstrap_p(totArrDep_ln,threads=5,xmax=1.3e+07)
bs_ln_p$p
```

The above curve and the estimated p_value indicate that airport popularity rank follows a Log-Normal distribution.